Palomar 5 Gaps

### 2024-09-12 paper/main.tex
added force on orbit figure
I now have Lz E
added mass size plane
added impact time to paper

  \begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{figures/Pal5_pouliasis2017pii-GCNBody_monte-carlo-009_suspects.png}
    \caption[]{This figure demonstrates how we determined which globular clusters were responsible for the gaps. The bottom plot showcases the evolution of the stream density in simulation time. The y-axis is $\tau$, which is a coordinate in units of time that indicates how far ahead or behind it is from a globular cluster. The x-axis is the simulation time, $t$, where 0~s km~kpc$^{-1}$ indicates present time. The density was used to determine a sutible length of the stream as a function of time. This length was then used to extract a piece of Palomar 5's orbit about a given position of Pal 5 in time. This orbital segment is used to approximate the stream. Then, the gravitational force from all other clusers was computed on the orbit. Moments of high acceleration indicate the passage of another cluster. The top 5 strongest passages are labeled with red circles as well as the name of the clusters. }
    \label{fig:profiles}
    \end{figure*}

@@

  \begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{figures/E_Lz_perturbers.png}
    \includegraphics[width=1\linewidth]{figures/mass_size_plane.png}
    \includegraphics[width=\linewidth]{figures/histogram_impact_time.png}
    \caption{One plot shows the distribution in energy and angular momentum, the next are the inernal proeprties of the clusters, and the last show when the clusters commit their crime, and how many times it happens accross the 50 simulations. }
    \label{fig:mass_size_plane}
    \end{figure}

>>>>

  \begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{force_on_orbit-monte-carlo-009.png}
    \caption[]{This figure demonstrates how we determined which globular clusters were responsible for the gaps. The bottom plot showcases the evolution of the stream density in simulation time. The y-axis is $\tau$, which is a coordinate in units of time that indicates how far ahead or behind it is from a globular cluster. The x-axis is the simulation time, $t$, where 0~s km~kpc$^{-1}$ indicates present time. The density was used to determine a sutible length of the stream as a function of time. This length was then used to extract a piece of Palomar 5's orbit about a given position of Pal 5 in time. This orbital segment is used to approximate the stream. Then, the gravitational force from all other clusers was computed on the orbit. Moments of high acceleration indicate the passage of another cluster. The top 5 strongest passages are labeled with red circles as well as the name of the clusters. }
    \label{fig:profiles}
    \end{figure*}

@@

  \begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{E_Lz_perturbers.png}
    \includegraphics[width=1\linewidth]{mass_size_plane.png}
    \caption{One plot shows the distribution in energy and angular momentum, the next are the inernal proeprties of the clusters, and the last show when the clusters commit their crime, and how many times it happens accross the 50 simulations. }
    \label{fig:mass_size_plane}
  \end{figure}

  \begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{histogram_impact_time.png}
    \caption{When the impacts occured}
    \label{fig:histogram_impact_time}
  \end{figure*}
